Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-30 paper.tex
Revise abstract

Layered systems with a lateral gradient in their refractive indices
and thicknesses may be employed for the development of a variety of
optical devices and
applications. They may be fabricated of porous silicon (PS) through a
position dependent electrochemical process. Thus, the possibility of
predicting the local current density $j$ and the co rresponding
porosity $p$
and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties with
ultraviolet-visible-near infrared reflectance
spectroscopy, \notaL{Should we mention microscopy?}, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
our model by comparing the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel nonhomogenous devices with lateral gradients which can be used
for manifold applications.

>>>>

A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, \notaL{Should we mention microscopy?}, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
our model by comparing the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel nonhomogenous devices with lateral gradients which can be used
for manifold applications.
